---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
```

```{r}
boardgames <- read_csv("raw_data/collection.csv")
my_ratings <- read_csv("raw_data/my_ratings.csv", locale = locale(encoding="latin1"))

dim(boardgames) # 59 rows 58 cols
names(boardgames) # lots of columns I'm not interested in

head(boardgames)
```

We've got the name of the boardgame, it's ID, lots of columns based on my own data about said
game (will remove for now). 
- baverage: geek rating
- average: average rating
- avgweight: i.e. how difficult game is to learn
- rank: rank in the bgg database
- numowned: how many bgg users own the game



```{r}
boardgames_trim <- boardgames %>% 
  select(objectname, average, avgweight, rank, numowned,
         playingtime, maxplayers, minplayers, bggrecagerange) %>% 
  rename(boardgame = objectname,
         average_bgg_rating = average,
         average_difficulty = avgweight,
         bgg_rank = rank,
         num_owned = numowned,
         max_players = maxplayers,
         min_players = minplayers,
         play_time = playingtime,
         rec_age_range_from = bggrecagerange) %>% 
  mutate(boardgame = str_to_title(boardgame)) %>% 
  arrange(boardgame) %>% 
  mutate(boardgame = str_remove(boardgame, " [:punct:] .+"),
         # remove dashes and  anything after as these caused issues
         rec_age_range_from = as.numeric(str_remove(rec_age_range_from, "\\+"))) %>% 
  # remove + from age range and make numeric
  mutate(average_players = (max_players + min_players)/2)
 # make a new column with number of players between min and max



boardgames_trim
```

Will join the datasets - challenge is that I named games differently to the bgg dataset.
```{r}
my_ratings <- my_ratings %>% 
  janitor::clean_names() %>% 
  mutate(game = str_to_title(game)) %>% 
  select(game, price_i_paid, my_rating, year_bought) %>% 
  arrange(game) %>% 
  mutate(game = str_remove(game, " [:punct:] .+"),
         game = str_remove(game, " $")) %>%  # remove dashes and
  # anything after as these caused issues
  filter(game != "Total") # remove total row from original spreadsheet 

my_ratings
```

Going to get a list of all games from each dataframe side by side for comparison:
```{r}
my_game_names <- my_ratings %>% 
  select(game) 
bgg_names <- boardgames_trim %>% 
  select(boardgame) 
# find which names aren't in one but are in the other
#setdiff(sort(bgg_names), sort(my_game_names))

# want to exclude expansions as standalone entries
expansions <- c("Root: The Exiles And Partisans Deck",
                "Root: The Riverfolk Expansion",
                "Root: The Underworld Expansion"
)

comparison <- boardgames_trim %>% 
  select(boardgame) %>% 
  filter(!(boardgame %in% expansions)) %>% 
  bind_cols(my_game_names) %>% 
  mutate(same = (boardgame == game)) %>% 
  filter(!same)
```

Based on this side-by-side comparison of boardgame names, will need to manually ensure the names match. Commas are the main issue, they look the same across datasets but seem to be different somehow.



```{r}
boardgames_combined <- boardgames_trim %>% 
  filter(!(boardgame %in% expansions)) %>% 
  full_join(my_ratings, by = c("boardgame" = "game"))
```



```{r}
boardgames_combined %>% 
  ggplot() +
  geom_histogram(aes(x = average_bgg_rating), fill = "indianred")
```


Missing data?
```{r}
boardgames_combined %>% 
  summarise(across(.cols = everything(), .fns = ~sum(is.na(.x))))
```
A few of my prices paid and ratings. The prices paid were gifts and the ratings were ones I haven't played enough to rate.

0s?
```{r}
boardgames_combined %>% 
  summarise(across(.cols = everything(), .fns = ~sum(.x == 0)))
```
2 BGG ranks are 0. Hmm

```{r}
boardgames_combined %>% 
  filter(bgg_rank == 0)
```

This is because they are not the standard edition and so BGG doesn't have a ranking - will use original rankings for base games from the site.

Everdell = 31
Tokaido = 703

```{r}
boardgames_combined <- boardgames_combined %>% 
  mutate(bgg_rank = case_when(
    boardgame == "Everdell: The Complete Collection" ~ 31,
    boardgame == "Tokaido Collector's Edition" ~ 703,
    .default = bgg_rank
  ))
```



Save data
```{r}
write_csv(boardgames_combined, "clean_data/boardgames_clean.csv")
```

